Active Object Search with a Mobile Device for the Visually Impaired

### 2018-11-23 paper.tex
Added navigation instruction paragraph

The app uses a 6$\times$6 discretised and wrapped radial grid to simplify the tracking and waypoint generation processes. A policy action is converted by the app into a new search waypoint centred on a cell of the radial grid, e.g.\ an `$UP$' action will generate a waypoint one grid cell above the current the camera's orientation. Note that this cell is not part of the MDP' state: the radial grid is only used to discretise the pan-tilt movements of the camera and to guarantee a minimum angular variations between subsequent actions. The grid is generated at the app's start-up and remains constant throughout its lifetime. The app then uses the new waypoint's location to provide the user with guidance instructions. The policy actions, and waypoints by extension, are given relatively to the current camera's pan-tilt orientation. The grid spans \SI{120}{\degree} in both the pan and tilt dimensions, giving a resolution of \SI{20}{\degree} per grid cell.

>>>>

The app uses a 6$\times$6 discretised and wrapped radial grid to simplify the tracking and waypoint generation processes. A policy action is converted by the app into a new search waypoint centred on a cell of the radial grid, e.g.\ an `$UP$' action will generate a waypoint one grid cell above the current the camera's orientation. Note that this cell is not part of the MDP' state: the radial grid is only used to discretise the pan-tilt movements of the camera and to guarantee a minimum angular variations between subsequent actions. The grid is generated at the app's start-up and remains constant throughout its lifetime. The app then uses the new waypoint's location to provide the user with guidance instructions. The policy actions, and waypoints by extension, are given relative to the current camera's pan-tilt orientation. The grid spans \SI{120}{\degree} in both the pan and tilt dimensions, giving a resolution of \SI{20}{\degree} per grid cell.

The position of the waypoint is given to the user by a set of guidance instructions (the arrows seen on-screen in Figure~\ref{fig:system-screenshot}) in terms of the actions defined in $\textbf{A}$. This might seem like an unnecessary extra step, but since we are designing this system for VI users who are limited to audio instructions. This makes it necessary to split the instructions up into separate channels that can be communicated more simply, especially so when one considers the bandwidth limitations of a human's audio channel as compared to the visual one.
